\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{hyperref}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Mehul Sharma}}\\
	\href{mailto:mehulcse0209@gmail.com}{mehulcse0209@gmail.com} $\cdot$  +91-8769883659 
	
\end{center}

% \begin{flushright}
% 	\textbf{Github}: & github.com/mehuled\\
% 	\textbf{Programming Languages}: & Go, Java
% \end{flushright}

%==== Experience ====%
\header{Experience}
\vspace{1mm}
\textbf{\href{http://razorpay.com/}{Razorpay}} \hfill Bengaluru, KA, India\\
\textit{Senior Software Development Engineer} \hfill Oct 2021 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 0.5pt
	\item Building and maintaining high scale (3000 rps) and low latency (5 ms) controlled feature roll-out and experimentation services that are used by multiple BUs to confidently do feature roll-outs.
	\item Developed golang SDK for in-house experimentation service to reduce friction in adoption and foster a culture of feature experimentation, led to 80 experiments being live from 0 baseline.
	\item Built experiment instrumentation feature to capture events funnel for different variants and conclude winning variant of an experiment. 
\end{itemize}
\textit{Software Development Engineer} \hfill May 2021 - Sep 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 0.5pt
	\item Built and evangelised dynamic user segmentation in the experimentation service, using bloom filter to support set-membership evaluation of upto 10M merchants in constant time.
	\item Actively contributed to uphold the engineering culture at Razorpay by contributing to in-house standard packages, collaborating with multiple teams to build the right solutions.
\end{itemize}
\textbf{\href{https://innovaccer.com/}{Innovaccer}} \hfill Noida, India\\
\textit{Software Development Engineer - Platform} \hfill Jun 2019 - May 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 0.5pt
	\item Built TBs scalabale data parsers and data standardisation modules for parsing CSV, HL7, CCDA, X12 and other healthcare specific data formats for the Data Platform.
	\item Designed and developed a framework to migrate existing Hadoop/Spark based implementation of the data processing engine to AWS Redshift and eventually to Postgres and thus made the platform ACID compliant and cost effective with 99.99\% availability.
\end{itemize}
\textbf{\href{https://opslyft.com/}{Opslyft}} \hfill San Francisco (Remote)\\
\textit{Software Development Engineer} \hfill Jan 2019 - May 2019\\
\vspace{-1mm}
\begin{itemize} \itemsep 0.5pt
	\item Conceived and built the first version of the product, used CUR reports with AWS Athena to provide customised dashboards to our customers with 1-click integration via Cloud Formation templates. Got us our first customer.
	\item Implemented features like RI right sizing, idle resources management, CLI integration to the product as per the feedback received from our initial customers.
\end{itemize}
\textbf{\href{https://innovaccer.com/}{Innovaccer}} \hfill Noida, India\\
\textit{Software Development Engineer (Intern) - Platform} \hfill May 2018 - July 2018\\
\vspace{-1mm}
\begin{itemize} \itemsep 0.5pt
	\item Built in-house logs archiving service by extracting and compressing application logs from our services and storing them onto AWS S3.
\end{itemize}


\header{Projects}
\vspace*{2mm}
{\textbf{NAND to Tetris}} {\sl Java, JVM, Assembly, HDL} \hfill \href{https://git.io/JUnui}{https://git.io/JUnui}  \\
Built a modern computer from first principles starting with a NAND gate, went on to write HDL for a ALU, an Assembler, a Compiler, JVM analogous virtual machine for a modern programming language called Jack.\\
\vspace*{2mm}
{\textbf{Voice assistant for Linux}} {\sl Python, AWS Lambda, Paramiko} \hfill \href{https://git.io/JUnuK}{https://git.io/JUnuK}\\
Implemented a voice-based assistant for my Linux machine by integrating AWS Lex, Alexa, AWS Lambda, Paramiko to execute remote calls on my Linux machine.\\
\vspace*{2mm}
\vspace*{2mm}

\header{Skills}
\vspace{2mm}
\begin{tabular}{ ll}
	\textbf{Programming Languages}: & Go, Java\\
	\textbf{Technologies}:           & Kubernetes, Microservices, Databases, Object Storage, AWS  \\
	\vspace{1mm}
\end{tabular}

%==== Education ====%
\header{Education}
\textbf{The LNM Institute of Information Technology, Jaipur}\hfill Jaipur, India\\
B.Tech Computer Science \& Engineering \hfill July 2015 - Jun 2019\\
	\vspace{2mm}
\textbf{Courses} : 
\textit{Design and Analysis of Algorithms, Compiler Design, Operating Systems, Computer Networks, DBMS, Wearable Computing, OOP, Consumer Psychology and others.}
\vspace{2mm}


\vspace*{2mm}

\ 
\end{document}
